### 2024-11-26 paper/paper.qmd
First draft of the paper

---
title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
subtitle: "Positive Effects of Pricing, Seats, Performances, and Holidays, with Limited Impact During Tony Award Months"
author: "Xuanel Zhou"
thanks: "Code and data are available at:https://github.com/Isazhou13/Broadway_Gross"
date: today
date-format: long
toc: true
abstract: "This study examines the key factors influencing Broadway’s weekly gross revenue using datasets from Playbill and The Broadway League. The result shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact gross, while Tony Award months show limited effects. Despite steady long-term growth, disruptions such as the 2016 snowstorm and COVID-19 highlight the industry’s vulnerability to external shocks. These findings provide actionable strategies, including holiday-focused marketing, and enhanced engagement during award seasons, to sustain growth and optimize Broadway’s financial performance."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(knitr)
library(arrow)
library(here)
library(scales)

analysis_data <- read_parquet(here("data", "02-analysis_data", "cleaned_broadway_grosses.parquet"))
```

# Introduction {#sec-introduction}

Broadway is a cultural and economic landmark in New York City, contributing significantly to the city's global reputation and economy. For stakeholders, understanding the drivers of Broadway revenue is essential, as it directly informs strategic decisions on pricing, scheduling, and resource allocation to maximize profitability and sustain operations. This study aims to identify and quantify the key factors influencing Broadway’s weekly gross revenue, using datasets provided by Playbill and The Broadway League.

The estimand in this paper represents the weekly gross revenue of Broadway shows. Specifically, it examines how variables such as ticket price, theater seating capacity, number of performances, whether it is a holiday week, whether it falls in a Tony Award month, and the year influence weekly gross revenue. While the true estimand is unknown, it is approximated using the available data and model assumptions. Defining the estimand ensures the model and methodology align with the research objective and facilitates addressing potential biases from data limitations or methodological choices.

The analysis, conducted using a multiple linear regression model, reveals that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway’s weekly gross revenue. Conversely, the limited impact of Tony Award months highlights opportunities for growth. While steady long-term growth is observed, disruptions such as the 2016 snowstorm and COVID-19 emphasize Broadway’s vulnerability to external shocks.

These findings emphasize both the opportunities and challenges Broadway faces in maximizing its revenue. Identifying the factors that drive revenue and highlighting periods of underperformance provide a foundation for adapting to evolving market conditions. For instance, additional potential can be realized through strategies such as holiday packages, collaborations with tourism boards, and enhanced on-site experiences. Addressing the low impact of Tony Award months could involve exclusive ticket packages and increased media engagement to leverage the event’s visibility. In an era of rapid digitalization and shifting consumer preferences, Broadway must innovate and adopt targeted strategies to sustain growth and maintain its position as a global cultural icon.

The remainder of this paper is structured as follows: @sec-data provides an overview of the dataset and visualizations of the variables. @sec-model-set-up details the modeling approach, including predictor selection and the regression model structure. @sec-results presents the primary findings and outcomes of the model. Finally, @sec-discussion explores the key findings, highlights the main takeaways, addresses the study's weaknesses, and outlines potential next steps.

# Data {#sec-data}

## Overview

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here] and scales [@scales]. The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets. **ggplot2** is used for data visualization, creating a range of plots to explore and present trends in the data. **knitr** facilitates the integration of analysis and reporting by generating dynamic reports in R Markdown. **arrow** is used for efficient handling of large datasets, particularly for reading and writing data in Parquet format to optimize storage and processing. The **here** package ensures reproducibility by standardizing file paths in the project directory, making it easier to locate and load data files. Finally, **scales** is employed to enhance the readability of plots by formatting axes, labels, and scales, ensuring clarity in the presentation of numeric and categorical data.

The dataset, sourced from **Playbill**, reflects Broadway weekly grosses as reported by theatres affiliated with The Broadway League. The data cleaning process involved grouping observations and removing missing values. The final dataset consists of 14,519 observations across 10 variables: `week_ending`, `week_number`, `weekly_gross`, `avg_ticket_price`, `seats_in_threatre`, `performances`, `year`, `month`, `holiday_week` and `Tony_Award`.

## Measurement and Considerations

The dataset for this study originates from Playbill, which collects information about Broadway shows through direct reporting and partnerships with industry organizations. A significant portion of the data, particularly box office grosses and performance metrics, is provided by The Broadway League, a national trade association for the Broadway industry.

The transformation of real-world phenomena into the dataset begins with data collection. The Internet Broadway Database (IBDB), managed by The Broadway League, compiles comprehensive records of Broadway productions from sources such as theater programs, which detail cast and crew information. Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records. This information is then processed into key metrics, including ticket sales, attendance, revenue, and theater utilization, which are published weekly. Before release, The League’s research department verifies the data’s accuracy and removes personal information to ensure privacy.

However, converting real-world phenomena into dataset entries inevitably results in the loss of important contextual details. For example, shows offering premium tickets or standing-room sales may disproportionately inflate weekly grosses compared to productions without these options. While the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, leaving gaps in understanding revenue dynamics. Similarly, discounts and promotions, such as rush tickets or group sales, can lower the average ticket price, potentially underestimating the perceived value of tickets sold. Additionally, while the dataset provides weekly metrics, it lacks details about whether performances occurred on weekdays or weekends, further limiting insights into revenue patterns. These limitations underscore the challenges of translating complex industry data into simplified metrics for analysis.

## Outcome variables

```{r}
#| label: fig-weekly_gross
#| fig-cap: Distribution of Broadway weekly gross.
#| echo: false

# Generate a histogram for Weekly Gross Revenue
ggplot(analysis_data, aes(x = weekly_gross)) +
  geom_histogram(binwidth = 100000, fill = "steelblue", color = "black", alpha = 0.7) +
  labs(
    x = "Weekly Gross ($)",
    y = "Number of Occurrences"
  ) +
  scale_x_continuous(labels = comma) +  # Format x-axis labels with commas
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14)
  )
```

The outcome variable of interest for this study is the weekly gross revenue for Broadway productions. The distribution, shown in @fig-weekly_gross, exhibits a right-skewed pattern. Most weeks have revenues ranging between $500,000 and $2,000,000, with a declining frequency as revenue increases. The mode of the distribution appears around $2,000,000. A small number of weeks report revenues exceeding $3,000,000, which may represent potential outliers or rare events that warrant further investigation. These high-revenue weeks could stem from unusual circumstances, such as special promotions, holiday seasons, or significant market shifts.

## Predictor variables

### Year

```{r}
#| label: fig-yearly
#| fig-cap: Yearly Gross Revenue Trends for Broadway Productions, spanning from 2010 to 2019.
#| echo: false
#| warning: false
#| message: false

# Aggregate data by year
data_yearly <- analysis_data %>%
  mutate(year = year(week_ending)) %>%  # Extract the year from the week_ending column
  group_by(year) %>%
  summarise(average_weekly_gross = mean(weekly_gross, na.rm = TRUE))  # Calculate yearly averages

# Create the plot
ggplot(data_yearly, aes(x = year, y = average_weekly_gross)) +
  geom_line(color = "steelblue", size = 1) +
  labs(
    x = "Year",
    y = "Average Yearly Gross ($)"
  ) +
  theme_minimal() +
  scale_x_continuous(  # Adjust scale for years
    breaks = seq(min(data_yearly$year), max(data_yearly$year), by = 1),  # One tick per year
    labels = scales::label_number(accuracy = 1)  # Show integer year labels
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.subtitle = element_text(hjust = 0.5, size = 12)
  )

```

@fig-yearly captures the Broadway industry's growth over the decade. The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year. The chart shows a steady increase in average yearly gross revenue, reflecting overall industry growth. From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2019. A slight dip in 2020 likely reflects the impact of the COVID-19 pandemic on Broadway operations.

```{r}
#| label: fig-week_ending
#| fig-cap: Weekly grossfor each Broadway show over time, spanning from 2010 to 2019. Each point represents the gross for a particular week for a specific show.
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data, aes(x = week_ending, y = weekly_gross)) +
  geom_point(color = "steelblue", size = 0.5, alpha = 0.7) +  # Replace geom_dot with geom_point
  labs(
    x = "Year",
    y = "Weekly Gross ($)",
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14)
  ) +
  scale_x_date(
    date_labels = "%Y",       # Show the year on the x-axis
    date_breaks = "1 year"    # Add a tick for each year
  ) +
  scale_y_continuous(labels = comma)  # Format y-axis labels with commas

```
@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $500,000 to $2,000,000, which aligns with the histogram results shown in @fig-weekly_gross. However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.

Earlier years (2010–2012) show a compact distribution of weekly gross. From 2015 onward, the range widens, with both higher peaks and broader variation between the lowest and highest values, reflecting increased performance variability among Broadway shows. Notably, some shows at some weeks after 2015 exceed $3,000,000, indicating more outliers and growing disparities between top-performing shows and others, likely influenced by audience preferences, pricing, and industry growth. These peaks are more commonly observed at the end of the year, suggesting a seasonal effect, likely tied to holiday demand and special events.

### Average price of tickets sold

```{r}
#| label: fig-avg_ticket_price
#| fig-cap: Distribution of Average Broadway Ticket Prices
#| echo: false

# Generate a histogram for avg_ticket_price 
ggplot(analysis_data, aes(x = avg_ticket_price)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "black", alpha = 0.7) +  # Customize bin width and colors
  labs(
    x = "Average Ticket Price ($)",
    y = "Number of Occurrences"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )
```
@fig-avg_ticket_price shows the majority of average ticket prices are concentrated around $100, with a peak frequency between $80 and $120. The right skewed distribution, indicating that while most ticket prices are relatively affordable, there are instances of higher ticket prices extending beyond $300, with a few exceeding $500.

### Theatre seat capacity

```{r}
#| label: fig-seats_in_theatre
#| fig-cap: Distribution of Theatre Sizes Based on Number of Seats
#| echo: false

# Generate a histogram for seats_in_theatre
ggplot(analysis_data, aes(x = seats_in_theatre)) +
  geom_histogram(binwidth = 50, fill = "steelblue", color = "black", alpha = 0.7) +  
  labs(
    x = "Number of Seats in the Theatre",
    y = "Number of Occurrences"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )

```

@fig-seats_in_theatre illustrates the distribution of theatre sizes on Broadway, measured by the number of seats. The most common theatre size is around 1,000 seats, with a significantly higher frequency compared to other sizes.

### Number of performances in the week

```{r}
#| label: fig-performances
#| fig-cap: Distribution of Performances
#| echo: false

# Generate a histogram for performances
ggplot(analysis_data, aes(x = performances)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "black", alpha = 0.7) + 
  scale_x_continuous(breaks = seq(0, max(analysis_data$performances, na.rm = TRUE), by = 1)) +  
  labs(
    x = "Number of Performances",
    y = "Number of Occurrences"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )

```
@fig-performances highlights the consistency in Broadway’s performance schedules, with the vast majority of shows performing 8 times per week, reaching a frequency of over 10,000 occurrences. A small number of shows have fewer or occasionally more than 8 performances per week, likely due to special events, holidays, or production adjustments.

### Holiday Week

```{r}
#| label: fig-holiday_week
#| fig-cap: Comparison of Average Weekly Gross Between Holiday and Non-Holiday Weeks
#| echo: false

# Convert holiday_week to a factor
analysis_data <- analysis_data %>%
  mutate(holiday_week = as.factor(holiday_week))  # Ensure holiday_week is treated as a categorical var
# Aggregate data to calculate average weekly gross for holiday and non-holiday weeks
aggregated_data_holiday <- analysis_data %>%
  group_by(holiday_week) %>%  # Group by holiday status
  summarise(avg_weekly_gross = mean(weekly_gross, na.rm = TRUE)) %>%  # Calculate average Weekly Gross
  mutate(holiday_week = case_when(
    holiday_week == 0 ~ "Non-Holiday Week",  # Rename 0 as "Non-Holiday Week"
    holiday_week == 1 ~ "Holiday Week"      # Rename 1 as "Holiday Week"
  ))

# Bar chart for average weekly gross
ggplot(aggregated_data_holiday, aes(x = holiday_week, y = avg_weekly_gross, fill = holiday_week)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```
Holiday weeks were identified based on the major holidays of the year and include the following:
New Year’s Week: The week containing January 1st.

- Independence Day Week: The week of July 4th.
- Labor Day Week: The week containing Labor Day, which falls on the first Monday of September.
- Thanksgiving Week: The week containing the fourth Thursday of November.
- Christmas Week: The week containing December 25th.

Non-holiday weeks are defined as all other weeks that do not overlap with these predefined holiday periods.

The weekly gross revenue was aggregated by grouping the data into holiday and non-holiday weeks. The average weekly gross revenue for each category was then calculated by summing all weekly gross revenues within the category and dividing by the total number of weeks in that category.

As shown in @fig-holiday_week, the average weekly gross revenue during holiday weeks is slightly higher than during non-holiday weeks, though the difference is relatively small. This suggests that holiday weeks may attract slightly larger audiences or higher ticket sales, due to increased leisure time and tourism. However, non-holiday weeks still maintain a comparable level of average weekly gross, demonstrating consistent revenue throughout the year.

### Tony Award Period

```{r}
#| label: fig-Tony_Award
#| fig-cap: Comparison of Weekly Gross Revenue During Tony Award and Non-Award Months
#| echo: false

# Aggregate data to calculate average weekly gross for Tony Award Period and off Period
aggregated_data_award <- analysis_data %>%
  group_by(Tony_Award) %>%  # Group by Tony Award status
  summarise(avg_weekly_gross = mean(weekly_gross, na.rm = TRUE)) %>%  # Calculate average Weekly Gross
  mutate(Tony_Award = case_when(
    Tony_Award == 0 ~ "Off-Award Month",     # Rename 0 as "Off-Award Month"
    Tony_Award == 1 ~ "Tony Award Month"    # Rename 1 as "Tony Award Month"
  ))

# Bar chart for average weekly gross
ggplot(aggregated_data_award, aes(x = Tony_Award, y = avg_weekly_gross, fill = Tony_Award)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    title = "Average Weekly Gross for Holiday vs Non-Holiday Weeks",
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```
The Tony Awards, formally the Antoinette Perry Award for Excellence in Broadway Theatre, are the highest honors in Broadway, typically held in June to mark the end of the Broadway season. Due to COVID-19, the 2020 awards were postponed to September.

The variable Tony Award Month refers to the month of the awards,  which often sees heightened media attention and anticipation. Off-Award Months include all other months, serving as a baseline for comparison.

Interestingly, @fig-Tony_Award shows that the average weekly gross revenue during off-award months is slightly higher than during the Tony Award month. This unexpected outcome may stem from factors like limited new production launches or audience focus shifting toward the awards themselves rather than attending shows.

# Model {#sec-model-set-up}

## Model Selection

Since the objective of this study is to help Broadway strategically manage and make decisions to increase gross revenue, it is crucial to select a model that effectively explains how various factors influence revenue. To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.

Simple Linear Regression is straightforward to implement, computationally efficient, and easy to interpret. It provides a clear understanding of the linear relationship between one independent variable and the dependent variable. However, the model is limited to analyzing the effect of a single predictor at a time and cannot account for the influence of multiple interacting variables. This oversimplification can lead to omitted variable bias in the context of a multivariable dataset like this one.

Despite Decision Trees excel at capturing non-linear relationships and interactions between variables, they are prone to overfitting, especially in moderately sized datasets, leading to poor generalization on unseen data.

Based on these considerations, **Multiple Linear Regression** was chosen. While it has limitations, such as reliance on key assumptions and sensitivity to outliers, MLR strikes a balance between simplicity, interpretability, and the ability to analyze the combined effects of multiple predictors. Its coefficients provide a clear quantification of the impact of each independent variable on weekly gross revenue, making it well-suited for understanding the underlying relationships in the data.

To ensure robust evaluation and avoid overfitting, the cleaned dataset was divided into training (70%) and testing (30%) subsets. The training set was used to fit the model, while the testing set was reserved for evaluating the model's performance on unseen data.

## Model Set-up

Key Assumptions:

- Linearity: The relationship between the dependent variable and each predictor is linear.
- Independence: Observations are independent of one another.
- Homoscedasticity: Variance of residuals is constant across all levels of the independent variables.
- Normality of Residuals: The residuals are normally distributed.
- No Multicollinearity: Independent variables are not highly correlated with each other.

Background details and diagnostics are included in [Appendix -@sec-model-details].

The model in this study is designed to predict weekly gross revenue using the following predictors:

- Average Ticket Price (`avg_ticket_price`): The average price of tickets sold during the week.
- Seats in the Theater (`seats_sold`): The seating capacity of the theater.
- Number of Performances (`performances`): The total number of performances held during the week.
- Holiday Week Indicator (`holiday_week`): Whether the show was performed during a holiday week (1 = holiday week, 0 = otherwise).
- Tony Award Month Indicator (`Tony_Award`) : Whether the show was performed during the Tony Award month (1 = Tony Award month, 0 = otherwise).
- Year (`year`):  The year in which the show was performed, ranging from 2010 to 2019.

The model takes the form:

\begin{align}
\text{weekly\_gross}_i &= \beta_0 + \beta_1 \cdot \text{avg\_ticket\_price}_i + \beta_2 \cdot \text{seats\_in\_theatre}_i \\
             &\quad + \beta_3 \cdot \text{performances}_i + \beta_4 \cdot \text{holiday\_week}_i \\ &\quad + \beta_5 \cdot \text{Tony\_Award}_i + \beta_6 \cdot \text{year}_i\epsilon_i \\
\epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align}

Where: 
\begin{align}
\beta_0 & \text{ is the intercept term} \\
\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 & \text{ are the coefficients for each predictor} \\
\sigma^2 & \text{ is the variance of the error term}
\end{align}

We run the model in R [@citeR] using the `stats` package from base R. The lm() function from this package was used to fit the multiple linear regression model.

## Interpretation of Coefficients

- Intercept ($\beta_0$): Represents the predicted value of the weekly gross revenue when all predictors are 0. Since it is unrealistic for all predictors the intercept serves as a theoretical starting point for the model. 
- Average Ticket Price ($\beta_1$): Measures the change in weekly gross revenue for each one-unit increase in average ticket price, assuming other predictors remain constant.
- Seats in the Theater ($\beta_2$):Represents the additional revenue associated with a one-unit increase in the seating capacity of the theater, holding other factors constant.
- Number of Performances ($\beta_3$): Indicates the increase in weekly gross revenue for each additional performance in the week, controlling for other variables.
- Holiday Week ($\beta_4$): Quantifies the difference in weekly gross revenue between holiday weeks and non-holiday weeks, all else being equal.
- Tony Award Month ($\beta_5$): Captures the difference in weekly gross revenue between weeks during the Tony Award month and other months, assuming other predictors remain unchanged.
- Year ($\beta_6$): Reflects the annual trend, representing the average change in weekly gross revenue for each one-year increase, controlling for other variables.

## Model justification

We expect a negative relationship between average ticket price and weekly gross revenue, as Broadway tickets are a form of entertainment and not a necessity. As ticket prices increase, demand is likely to decrease significantly because consumers may prioritize essential expenses over discretionary spending, especially for shows that are not well-known or during off-peak periods.

The seating capacity of the theater and the number of performances are also expected to have a positive relationship with weekly gross revenue, as larger venues or more performances each week can accommodate more audience members, resulting in higher total revenue.

For holiday weeks, we predict a positive effect on weekly gross revenue, as holidays often bring increased audience demand due to leisure time and tourism. Conversely, the effect of Tony Award months is less certain, as the difference in average weekly gross revenue during Tony Award months compared to other months is minimal.

Finally, the year variable is included to account for long-term trends, with an expected positive effect reflecting the steady growth of Broadway's gross revenue over the years.

# Results {#sec-results}

The results of the multiple linear regression model is summarized in the @tbl-modelresults. The result matches with some of our expectations while deviating in other areas.

As anticipated, average ticket price, seating in yheater, and number of performances exhibit significant positive relationships with weekly gross revenue. Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth. Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences.

The findings for holiday weeks also meet initial expectations, showing a positive relationship with weekly gross revenue. This result suggests that increased demand during holiday periods effectively boosts ticket sales, contributing to higher overall revenue.

However, the results for Tony Award months diverge from our initial expectations. Contrary to the assumption that Tony Award months would boost revenue due to increased demand or publicity, the coefficients for these variables are negative, indicating a slight decrease in weekly gross revenue during these periods.

Lastly, the year variable exhibits a small but positive effect, consistent with the expectation of a gradual upward trend in Broadway revenue over the years. This reflects the broader growth of the industry, potentially due to factors such as inflation. Overall, the model confirms some of our hypotheses while highlighting areas where the data does not fully align with expectations, prompting further discussion and exploration in the next section.

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: Regression Results for Weekly Gross. This table displays the coefficients, standard errors, and t-statistics for the multiple linear regression model used to analyze the factors influencing weekly gross for Broadway.  
#| warning: false

# Load the regression model
regression_model <- readRDS(here::here("models/regression_model.rds"))
summary <- summary(regression_model)

# Extract the coefficients and form a table with estimates, standard errors, and t-values
coefficients_table <- as.data.frame(summary$coefficients[, 1:3])

# Rename the columns
colnames(coefficients_table) <- c("Coefficient", "Standard Error", "t-Statistic")

# Display the table
kable(coefficients_table, digits = 2)

```

# Discussion {#sec-discussion}

## Key Findings {#sec-first-point}

This paper presents a multiple linear regression analysis to examine the factors influencing weekly gross on Broadway. Key predictors, including average ticket price, seating capacity, and number of performances, were found to significantly impact revenue, while holiday weeks and Tony Award months showed unexpected or non-significant effects. These findings highlight the complexity of audience behavior and the importance of operational decisions in optimizing revenue.

## Balancing Pricing, Seating Capacity, and Performance Frequency

Operational strategies such as ticket pricing, seating capacity, and performance frequency emerged as key drivers of weekly gross revenue, offering actionable opportunities for Broadway to increase earnings. The strong impact of average ticket price underscores the importance of implementing demand-based pricing strategies, particularly for popular or limited-run productions, where higher ticket prices can significantly boost revenue with minimal impact on attendance. For less popular shows, optimizing affordability could help maintain audience retention while still contributing to overall revenue.

Similarly, maximizing theater utilization through strategic scheduling and venue allocation is crucial for increasing revenue. Larger venues and additional performances can expand audience capacity, but Broadway managers must evaluate whether demand can sufficiently meet the increased supply. Additionally, managers must balance these strategies with logistical considerations such as performer availability, production costs, and preserving the quality of the audience experience. By carefully aligning pricing strategies with capacity optimization, Broadway can enhance revenue while ensuring sustainable long-term growth.

## Opportunities in Holiday Weeks and Tony Award Months

The model results indicate that while holiday weeks align with the expectation of increased revenue due to higher audience availability, the effects of Tony Award months challenge the assumption that they inherently boost revenue through increased media attention.

During holiday weeks, families often travel or engage in special outings. New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, holiday markets, and the New Year’s Eve Ball Drop in Times Square. This festive atmosphere draws millions of tourists, creating a significant opportunity for Broadway to boost gross revenue and position itself as a must-visit holiday experience.

To maximize this potential and leverage its prime location, Broadway could adopt targeted strategies to make attending shows more convenient and appealing for holiday visitors. For example, collaborating with hotels, travel agencies, and tourism boards to create holiday packages that include show tickets could firmly establish Broadway as an essential part of the holiday itinerary. Additionally, enhancing the on-site experience with seasonal concessions and festive elements could further help Broadway attract more visitors during this lucrative season.

For Tony Award months, the data indicates that Broadway gross remains unaffected, challenging the belief that the awards inherently drive revenue through increased media attention. While the Tony Awards generate significant publicity, the focus tends to be on a limited number of nominated or winning shows, leaving many other shows relatively unnoticed. This concentrated attention may not translate into broader attendance increases across the industry. To address this, Broadway could collaborate with media outlets to feature live broadcasts, behind-the-scenes content, and interviews with nominees to create excitement around both the awards and the shows themselves. Offering exclusive ticket packages for Tony-nominated shows during the awards season could further incentivize attendance and increase revenue.

## Sustaining Broadway’s Growth in a Rapidly Changing World

The significant positive relationship between year and weekly gross revenue reflects the steady growth of Broadway over the past decade, driven by factors such as rising ticket prices, increased tourism, and the industry’s ability to attract global audiences. However, this growth trajectory also have some exceptional cases, and not valid for all time period. For instance, the sharp decline in 2016 weekly gross during winter was influenced by a severe snowstorm that forced theaters to close, disrupting public transportation and preventing both audiences and performers from attending. Similarly, the slight downturn in 2019 coincided with the onset of the COVID-19 pandemic, which had a profound impact on Broadway operations, highlighting the industry’s vulnerability to external shocks.

Even with a generally positive and sustainable long-term growth trend, Broadway must adapt and innovate to keep pace with the rapid changes in today’s society. The rise of streaming platforms and the growing popularity of short-form video content present new challenges to live theater, demanding fresh approaches to attract and engage modern audiences. By embracing digital innovations while emphasizing the unique, immersive experience of live performances, Broadway can maintain its growth and continue thriving as a global cultural hub.

## Weaknesses

While the paper provides valuable insights into revenue drivers, it primarily focuses on direct factors such as ticket price, seating capacity, and performance frequency. The dataset lacks critical information such as marketing efforts, show popularity, repeat attendance rates, or audience demographics. As a result, the analysis misses deeper insights into other potential variables that could offer a more comprehensive understanding of revenue dynamics.

The model assumes linear relationships between predictors and weekly gross revenue. However, factors such as ticket price or performance frequency may demonstrate diminishing returns or threshold effects that are not reflected in the analysis. Furthermore, complex interactions between variables are not explored. For instance, changes in ticket price could influence consumers' willingness to buy, potentially altering demand and revenue in ways a linear model cannot fully capture.

Additionally, the model assumes uniform effects of predictors across all Broadway shows, which may oversimplify the analysis. Different types of productions (e.g., musicals, plays, blockbusters, or niche shows) likely have distinct revenue dynamics that are not adequately addressed by a single model.

Moreover, the model does not account for external factors such as economic conditions, competitor pricing, or shifts in tourism trends, all of which could significantly influence Broadway revenue. These omissions limit the model's ability to fully explain variations in weekly gross revenue and highlight areas for future improvement.

Another weakness of this study is its exclusive focus on analyzing gross revenue without considering the associated costs of producing and running Broadway shows. While understanding revenue drivers is crucial, gross revenue alone does not provide a complete picture of financial performance. Factors such as production expenses, marketing costs, theater rental fees, and operational overhead significantly impact profitability but are not accounted for in this analysis. Ignoring costs limits the ability to assess the net financial health of Broadway productions and could lead to incomplete or misleading conclusions about the success of certain strategies or shows.

## Next Steps

Incorporating additional variables, such as marketing expenditures, customer demographics, and customer experiences, could provide a deeper understanding of the factors influencing revenue. These information could be gathered in the future through detailed surveys aimed at collecting data on audience preferences, spending habits, and satisfaction levels. With this information, Broadway could develop more targeted marketing strategies tailored to different audience groups, allowing for customized promotions, pricing models, and programming that better address the unique needs of each segment, ultimately maximizing engagement and revenue.

Future analyses could also employ more advanced models to address the limitations of linear assumptions. For example, exploring non-linear relationships and interaction effects between variables, such as the interplay between ticket prices and theater size or the varying impact of holiday weeks on revenue, could reveal important dynamics.

Additionally, conducting separate analyses for different types of productions, such as traditional shows versus new or experimental productions, would help identify the unique revenue drivers for each category. This segmentation would enable more precise strategy recommendations tailored to the specific needs and performance characteristics of different types of Broadway shows. Also, combining these advanced analyses with cost considerations would offer a holistic approach to optimizing Broadway’s economic sustainability.

\newpage

\appendix

# Appendix: Idealized Methodology and Survey {#sec-Appendix1}

## Objective and Overview

The purpose of this appendix is to outline an idealized methodology and survey design to supplement the current analysis of Broadway’s weekly gross revenue. By incorporating additional survey data and addressing gaps in the existing dataset, this methodology aims to enhance the understanding of revenue drivers, audience behaviors, and market dynamics. The survey is designed to capture demographic, behavioral, and experiential data that complement the operational metrics already analyzed in the study.

## Core Objectives

- To gather audience demographics (e.g., age, income, location) to understand their influence on ticket purchases and attendance patterns. This information can be integrated into the model to enhance its predictive accuracy.
- To identify purchasing behaviors, such as repeat attendance, pricing sensitivity, and group sales, providing a foundation for refining marketing and pricing strategies.
- To assess audience motivations and satisfaction, focusing on factors driving show selection and overall theater experience, offering guidance on how to improve Broadway’s organizational and operational strategies.

## Sampling Strategy

Our sampling strategy utilizes **random sampling** to ensure unbiased representation of Broadway audiences. This approach randomly selects participants from the overall population of Broadway ticket buyers and attendees, minimizing potential biases and ensuring the sample reflects the diversity of the audience.

Random sampling provides a robust foundation for generalizable analysis, capturing a wide range of perspectives and behaviors without targeting specific subgroups. By employing this method, the study aims to produce reliable and comprehensive insights into the factors influencing Broadway’s attendance and revenue dynamics.

A minimum sample size of 1,000 responses per quarter is proposed to ensure statistical robustness across strata and account for seasonality.

## Recruitment Strategy

Participants will be recruited through a combination of:

- **In-Theater Surveys**: Surveys distributed at participating Broadway theaters, targeting audiences immediately after the performance for real-time feedback.
- **Online Platforms**: Email invitations to ticket buyers, links embedded in ticket purchase confirmations, and social media outreach via official Broadway channels.
- **Tourism Partnerships**: Collaborations with NYC tourism boards, hotels, and travel agencies to engage out-of-town visitors.
- **Incentives**: Offering discounts on future ticket purchases or exclusive merchandise as incentives for survey participation.

## Data Validation and Quality Assurance

- **Data Triangulation**: Responses will be cross-referenced with transactional data from ticket sales to validate self-reported behaviors.
- **Pretesting**: Pilot surveys will be conducted to test question clarity, response rates, and overall survey design effectiveness.
- **Anonymity and Privacy**: Personal data will be anonymized to encourage honest responses and comply with privacy regulations.

## Survey Design Considerations
The survey is designed to be comprehensive but concise, ensuring high response rates while capturing actionable data. Key design considerations include:

- **Question Types**: A mix of multiple-choice, Likert scale, and open-ended questions to balance structured data collection with qualitative insights.
- **Clarity**: Simple, jargon-free language to ensure accessibility for diverse audiences.

**Focus Areas:**

- Demographics: Age, income, location, gender, and education level.
- Attendance Behavior: Frequency of attendance, motivations, and purchasing habits.
- Experience Metrics: Satisfaction levels, likelihood of future attendance, and feedback on show quality.
- Pricing Sensitivity: Perceptions of ticket affordability and willingness to pay for premium experiences.

### Broadway Audience Survey Form

**Introduction:**

Thank you for taking the time to participate in this survey. Your feedback will help us understand Broadway audiences better and improve the overall experience.

Please Note:

- All responses will be kept strictly confidential.
- Your participation is entirely voluntary.
- We kindly request that you answer all questions honestly and to the best of your knowledge.
- The survey is estimated to take approximately 10 minutes to complete.
- If you have any inquiries or concerns regarding this survey, please don’t hesitate to contact the research team at **isabella.zhou@mail.utoronto.ca**.

Your contribution to this study is greatly appreciated! Each participant will be entered into a lottery with a chance to win a **$100 gift card redeemable for any Broadway show of your choice**.

**Section 1: About You**

What is your age ?

- Under 18
- 18–24
- 25–34
- 35–49
- 50–64
- 65 or older

What sex were you assigned at birth, on your original birth certificate?

- Female
- Male

How do you currently describe yourself (mark all that apply)?

- Female
- Male
- Transgender 
- I use a different term [free-text]

Where do you currently live?

- Manhattan
- Brooklyn
- Queens
- Bronx
- Staten Island
- Other New York City Borough: ____________
- Outside NYC (please specify): ____________

What is your annual household income (before taxes)?

- Less than $25,000
- $25,000–$49,999
- $50,000–$74,999
- $75,000–$99,999
- $100,000–$149,999
- $150,000–$249,999
- $250,000 or more

How far in advance do you typically purchase Broadway tickets?

- Less than a week
- 1–2 weeks
- 3–4 weeks
- 1–2 months
- 3 months or more

**Section 2: Broadway Attendance and Ticket Purchases**

How many Broadway shows have you attended in the past 12 months?

- None
- 1–2
- 3–5
- 6–10
- 11 or more

Have you seen this show before?

- Yes
- No

What motivates you to attend Broadway shows? (Check all that apply)

- Specific performers
- Storyline or theme of the show
- Award recognition (e.g., Tony Awards)
- Recommendations from friends or family
- Discounts or promotions
- Other (please specify): ____________

How much did you pay for your most recent Broadway ticket (including fees)?

- Less than $99
- $100–$149
- $150–$199
- $200–$249
- $250–$299
- $300–$349
- $350 or more

How do you usually purchase tickets?

- Online via website or app
- At the theater box office
- Through group sales or subscriptions
- Other (please specify): ____________

**Section 3: Experience and Preferences**

How satisfied were you with the last Broadway show you attended?

- Very satisfied
- Satisfied
- Neutral
- Dissatisfied
- Very dissatisfied

What factors most influenced your satisfaction? (Check all that apply)

- Quality of performance
- Cast or performers
- Theater amenities (e.g., seating, concessions)
- Ticket price relative to experience
- Other (please specify): ____________

What would improve your Broadway experience? (Check all that apply)

- Lower ticket prices
- Easier ticket access
- More diverse productions
- Enhanced theater amenities
- Other (please specify): ____________

When do you typically attend Broadway shows? (Check all that apply)

- Weekdays
- Weekends
- Holiday weeks (e.g., Thanksgiving, Christmas, New Year’s Week, (please specify): ____________
- Tony Award months (typically June)

Where do you typically hear about Broadway shows? (Check all that apply)

- Social Media (e.g., Instagram, Facebook, Twitter)
- Online ads or newsletters
- Word of mouth
- Print media (e.g., newspapers, magazines)
- Other (please specify): ____________

**Section 4: Future Engagement**

How likely are you to attend another Broadway show in the next 6 months?

- Very likely
- Somewhat likely
- Neutral
- Somewhat unlikely
- Very unlikely

What factors might prevent you from attending more Broadway shows?

- High ticket prices
- Lack of time
- Lack of interest in available productions
- Other (please specify): ____________

What additional suggestions do you have to improve the Broadway experience?

**End Message:**

Thank you for participating! Your feedback will play a vital role in enhancing the Broadway experience for future audiences. If you have any questions about this survey or would like to be informed about the results, please contact **isabella.zhou@mail.utoronto.ca**

\newpage

# Appendix: Additional Broadway Surveys and Data {#sec-Appendix2}

Besides the dataset used for this study, Broadway also conducts several key surveys to gather comprehensive data on various aspects of Broadway theatre. However, the information and datasets collected through these surveys are not publicly accessible for analysis. If this data were made available, merging it with the current dataset could provide a more robust model for gross analysis. These surveys include **The Demographics of the Broadway Audience**, which is designed to provide insights into the composition and behavior of Broadway theatregoers.

- **Sampling Method**: The survey is typically conducted annually, with performances selected quarterly to ensure a representative sample of Broadway's diverse offerings. This approach captures seasonal variations in the audience and provides a balanced dataset
- **Recruitment Method**: 
  - In-Person Distribution: Questionnaires are handed out to audience members during selected performances.
  - Online Access: Audiences can complete the survey online via a QR code provided at performances or through a link sent post-event.
  - Wi-Fi Login Prompt: Patrons connecting to a theatre’s Wi-Fi are also invited to participate in the survey.
These varied recruitment strategies aim to ensure a high response rate and broad representation of attendees.

Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway. These surveys and studies help capture broader insights into Broadway's influence and reach, contributing to a more comprehensive understanding of its role in the cultural and economic landscape.

\newpage

# Appendix: Model details {#sec-model}

## Diagnostics

```{r}
#| echo: false
#| label: fig-diagnosis-1
#| fig-cap: Diagnostic Plots for Regression Model Residuals. Residuals vs Fitted values, Q-Q Plot of residuals, Scale-Location plot, and Residuals vs Leverage, used to assess the assumptions of the multiple linear regression model.
#| warning: false
#| message: false
#| fig.width: 10
#| fig.height: 7

par(mfrow = c(2, 2))  
plot(regression_model)
```

As shown in @fig-diagnosis-1, these diagnostic plots indicate potential violations of the linear regression assumptions, suggesting the need for model refinements or transformations.

The curved pattern in the Residuals vs Fitted plot points to possible non-linearity, while the tails in the Q-Q plot highlight deviations from normality. Additionally, the trend observed in the Scale-Location plot suggests heteroscedasticity. Furthermore, the Residuals vs Leverage plot reveals points with high leverage and large residuals, indicating potential outliers that may disproportionately influence the model.

\newpage
## Mean Squared Error and Mean Absolute Error on Test Data

```{r}
#| echo: false
#| label: tbl-MSE
#| tbl-cap: Calculate Mean Squared Error (MSE) on Test Data
#| warning: false
#| message: false

# Load the test dataset
analysis_data_test <- read_parquet(here("data", "02-analysis_data", "broadway_grosses_test_data.parquet"))

# Predicted and actual values
predicted_values <- predict(regression_model, newdata = analysis_data_test)
actual_values <- analysis_data_test$weekly_gross

# Calculate evaluation metrics
# Mean Squared Error (MSE)
mse <- mean((predicted_values - actual_values)^2)

# Mean Absolute Error (MAE)
mae <- mean(abs(predicted_values - actual_values))

# R-squared
ss_total <- sum((actual_values - mean(actual_values))^2) # Total sum of squares
ss_residual <- sum((predicted_values - actual_values)^2) # Residual sum of squares
r_squared <- 1 - (ss_residual / ss_total)

# Combine metrics into a data frame for display
metrics_df <- data.frame(
  Metric = c("Mean Squared Error (MSE)", "Mean Absolute Error (MAE)", "R-squared"),
  Value = c(
    comma(round(mse, 2)),          # Format MSE with commas and 2 decimals
    comma(round(mae, 2)),          # Format MAE with commas and 2 decimals
    round(r_squared, 2)            # Format R-squared to 2 decimals
  )
)

# Display the metrics in a readable table format
kable(metrics_df, caption = "Model Performance Metrics", format = "markdown")

```

From @tbl-MSE, MSE measures the average squared prediction error. MAE represents the average prediction error magnitude. R-squared indicates that the model explains 83% of the variance in weekly gross revenue.

## Multicollinearity Check on the Training Data

```{r}
#| echo: false
#| label: fig-correlation
#| fig-cap: Correlation Matrix between variables
#| warning: false
#| message: false

library(corrplot)
analysis_data_train <- read_parquet(here("data", "02-analysis_data", "broadway_grosses_train_data.parquet"))

# Calculate the correlation matrix
cor_matrix <- cor(analysis_data_train[, c("avg_ticket_price", "seats_in_theatre", "performances", "holiday_week", "Tony_Award", "year")], use = "complete.obs")

# Rename the row and column names of the correlation matrix to remove underscores
colnames(cor_matrix) <- gsub("_", " ", colnames(cor_matrix))
rownames(cor_matrix) <- gsub("_", " ", rownames(cor_matrix))

# Create a beautiful correlation plot with modified labels
corrplot(
  cor_matrix, 
  method = "color",      
  type = "upper",        
  addCoef.col = "black", 
  tl.col = "black",      
  tl.srt = 45,          
  number.cex = 0.8,      
  col = colorRampPalette(c("red", "white", "blue"))(200) )

```

In @fig-correlation, a correlation check is performed. The matrix confirms the assumption of low multicollinearity among predictors, supporting the reliability of coefficient estimates in the regression model.

# Additional Visulization
```{r}
#| label: fig-facet-by-year
#| fig-cap: Average Weekly Gross Revenue Trends Across Months, spanning from 2010 to 2019.
#| echo: false
#| warning: false
#| message: false
# Facet the plot by Year

# Aggregate by month
data_monthly <- analysis_data %>%
  mutate(month = floor_date(week_ending, "month")) %>%
  group_by(month) %>%
  summarise(average_weekly_gross = mean(weekly_gross, na.rm = TRUE))

data_monthly <- data_monthly %>%
  mutate(
    year = year(month),                        # Extract year
    month_label = month(month, label = TRUE)  # Extract month name (label)
  )

# Create the faceted plot
ggplot(data_monthly, aes(x = month_label, y = average_weekly_gross, group = year)) +
  geom_line(color = "blue", size = 1) +
  labs(
    x = "Month",
    y = "Average Weekly Gross Revenue ($)"
  ) +
  theme_minimal() +
  facet_wrap(~ year, ncol = 3) + # Facet by year, 3 columns
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14)
  )

data_monthly <- data_monthly %>%
  mutate(year = as.factor(year))  # Convert year to a factor

```
\newpage

# Acknowledgements

Thanks to Open AI and ChatGPT 4o is used to write the paper.

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here] and scales [@scales].

# References

### 2024-11-28 other/datasheet/datasheet_Broadway.qmd
Add Datasheet for Broadway Gross Dataset

---
title: "Datasheet for Broadway Gross Dataset"
subtitle: "The dataset used for 'Understanding Broadway Gross: Key Factors and Growth Strategie'"
author: 
  - Xuanle Zhou
thanks: "Code and data are available at: https://github.com/Isazhou13/Broadway_Gross"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable the analysis of weekly gross revenue for Broadway productions. While it does not address a specific gap, it provides a structured repository of gross data that is valuable for understanding industry trends and evaluating show performance.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The specific creators of the dataset have not been explicitly identified. However, it is likely associated with The Broadway League and their Internet Broadway Database (IBDB), the official archive for Broadway theatre information. IBDB serves as a comprehensive resource for historical and current Broadway data.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Information regarding the funding source for the creation of the dataset is not currently available. However, The Broadway League operates in partnership with entities such as Chase and The New York Times, which may have contributed to its initiatives.
4. *Any other comments?*
    -  No further comments at this time.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance represents the information for a single production during a specific week.
2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset contains a total of 47,524 instances.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	-  The dataset includes all available instances of weekly gross data for Broadway productions in New York City, as collected by The Broadway League.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*

  - week_ending: 	Date of the end of the weekly measurement period. Always a Sunday.
  -week_number: Week number in the Broadway season. The season starts after the Tony Awards, held in early June. Some seasons have 53 weeks.
  - weekly_gross_overall: Weekly box office gross for all shows
  - show: Name of show. Some shows have the same name, but multiple runs.
  - theatre: Name of theatre. Only shows most recent theatre for shows that started at one theatre and moved to another (e.g., The Lion King will show Minskoff Theatre even though it played at New Amsterdam Theatre from 1997-2006).
  - weekly_gross: Weekly box office gross for individual show
  - potential_gross: Weekly box office gross if all seats are sold at full price. Shows can exceed their potential gross by selling premium tickets and/or standing room tickets.
  - avg_ticket_pric: Average price of tickets sold
  - top_ticket_price: Highest price of tickets sold
  - seats_sold: Total seats sold for all performances and previews
  - seats_in_theatre: Theatre seat capacity
  - pct_capacity: Percent of theatre capacity sold. Shows can exceed 100% capacity by selling standing room tickets.
  - performances: Number of performances in the week
  - previews: Number of preview performances in the week. Previews occur before a show's official open.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No specific label or target is explicitly assigned to each instance
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some information is missing from individual instances. Specifically, data on potential gross is unavailable for dates prior to July 1997. This is because Broadway productions did not calculate or record this information before that time.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No explicit relationship available 
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	-  No recommended data splits available
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There is no errors, sources of noise, or redundancies in the dataset
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is primarily self-contained but may reference external resources like theater locations or production details available via the Internet Broadway Database (IBDB). These resources are managed by The Broadway League, and their availability over time cannot be guaranteed without archival support.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- No further comments

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data is directly collected through observable metrics.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The specifics of this process have not been disclosed.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset represents the complete set of data and is not a sample from a larger collection.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Staff from organizations, including theater managers, producers, and accountants, are responsible for the data collection process. They are paid by salary. 
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- According to The Broadway League, they began recording weekly gross data in 1979. However, it is unclear whether they recorded the additional information found in the dataset during that time. The dataset contains detailed weekly gross data starting from the first week of July 1985.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- I downloaded the data from a publicly available GitHub repository, which sourced the information from the Playbill website. The link for the GitHub is: https://github.com/tacookson/data/tree/master/broadway-grosses
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- For tickets purchased online, users are presented with terms and conditions when creating an account. However, it remains unclear how information from previous years was collected or whether individuals were notified during that process.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Consent is inherently granted through the membership agreement with The Broadway League. By accepting the terms of membership, individuals agree to submit their data and allow its use for industry analysis and reporting.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Yes, the privacy policy states: "We may share your Personal Information with third parties for third-party marketing purposes. You can opt out of this by emailing us at league@broadway.org."
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No. 
12. *Any other comments?*
	- No further comments

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, the data cleaning for this study is complete. The raw data included a week_ending column that combined the year, month, and date into a single cell. To address this, the code was used to separate these elements into distinct columns. Unnecessary columns for this study, such as `weekly_gross_overall`, `show`, `theatre`, `potential_gross`, `top_ticket_price`, `seats_sold`, `pct_capacity`, and `previews`, were removed.
	 A new column, `holiday_week`, was created, with values marked as 1 for weeks corresponding to Independence Day, Labor Day, Thanksgiving, Christmas, and New Year's Week. Additionally, a `Tony_Awards` column was constructed to indicate whether a given month corresponds to the Tony Awards period. The Tony Awards is a prestigious theater award typically held in June. Moreover, the data is limited to the most recent decade, specifically from 2010 to 2020. Unreasonable values were filtered out, such as shows with an average ticket price of 0.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes. The raw data is saved. It can be accessed at: https://github.com/tacookson/data/blob/master/broadway-grosses/grosses.csv
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used is R Programming Language. 
4. *Any other comments?*
	-  No further comments

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, the dataset is publicly available and has been used in many papers for analysis.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No. 
3. *What (other) tasks could the dataset be used for?*
	- Some tasks using the dataset involve more detailed analyses of gross changes for particular shows.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Since the data is filtered from 2010 to 2020, it is recommended to evaluate whether this time frame is appropriate for future detailed analyses.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No, there are no tasks for which the dataset should not be used.
6. *Any other comments?*
	- No further comments.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is publicly available through GitHub repositories.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is available from GitHub, following link of: https://github.com/tacookson/data/tree/master/broadway-grosses
3. *When will the dataset be distributed?*
	- The dataset was published in April 2020.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No. 
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No. 
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No. 
7. *Any other comments?*
	- No further comments.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The GitHub repository owner or contributors hosting the dataset typically maintain it, with the original data provided by The Broadway League.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact the owner by creating an issue on the GitHub repository. Additionally, the owner’s website homepage includes contact information. The owner's email is alexander.cookson@gmail.com, and their LinkedIn profile can be accessed at https://www.linkedin.com/in/alexcookson/.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No. 
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- It does not provide information regarding this issue.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Retention limits are determined by The Broadway League's policies.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- There is no information regarding this issue.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- They can contact the Internet Broadway Database using the form available at https://form.jotform.com/broadwayleague/ibdb-contact-form. This form can be used to contact Broadway with questions or to provide additional information. However, any updates made may only be reflected in the Broadway database and not in the GitHub repository.
8. *Any other comments?*
	- No further comments.

\newpage

# References

### 2024-11-28 paper/paper.qmd
Revise the Prose for paper

@@
 
-The analysis, conducted using a multiple linear regression model, reveals that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway’s weekly gross revenue.
+The analysis, conducted using a multiple linear regression model, shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway’s weekly gross revenue.
 Conversely, the limited impact of Tony Award months highlights opportunities for growth.
@@
 For instance, additional potential can be realized through strategies such as holiday packages, collaborations with tourism boards, and enhanced on-site experiences.
-Addressing the low impact of Tony Award months could involve exclusive ticket packages and increased media engagement to leverage the event’s visibility.
+To address the low impact of Tony Award months, strategies could include offering exclusive ticket packages and enhancing media engagement to capitalize on the event's visibility.
 In an era of rapid digitalization and shifting consumer preferences, Broadway must innovate and adopt targeted strategies to sustain growth and maintain its position as a global cultural icon.
@@
 The transformation of real-world phenomena into the dataset begins with data collection.
-The Internet Broadway Database (IBDB), managed by The Broadway League, compiles comprehensive records of Broadway productions from sources such as theater programs, which detail cast and crew information.
+The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information.
 Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records.
@@
 Similarly, discounts and promotions, such as rush tickets or group sales, can lower the average ticket price, potentially underestimating the perceived value of tickets sold.
-Additionally, while the dataset provides weekly metrics, it lacks details about whether performances occurred on weekdays or weekends, further limiting insights into revenue patterns.
+Additionally, although the dataset includes weekly metrics, it does not specify whether performances took place on weekdays or weekends, limiting the analysis of gross patterns.
 These limitations underscore the challenges of translating complex industry data into simplified metrics for analysis.
@@
 - Christmas Week: The week containing December 25th.
+- New Year's Week: The week of the January 1st.
 
@@
 
-Since the objective of this study is to help Broadway strategically manage and make decisions to increase gross revenue, it is crucial to select a model that effectively explains how various factors influence revenue.
-To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.
+The objective of this study is to assist Broadway in strategically managing and making decisions to increase gross revenue, making it essential to choose a model that accurately explains the factors influencing revenue.To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.
 
@@
 This reflects the broader growth of the industry, potentially due to factors such as inflation.
-Overall, the model confirms some of our hypotheses while highlighting areas where the data does not fully align with expectations, prompting further discussion and exploration in the next section.
+Overall, the model confirms some hypotheses while highlighting discrepancies in the data, prompting further discussion and analysis in the next section.
 
@@
 
-Similarly, maximizing theater utilization through strategic scheduling and venue allocation is crucial for increasing revenue.
+Maximizing theater utilization through strategic scheduling and venue allocation is key to increasing revenue.
 Larger venues and additional performances can expand audience capacity, but Broadway managers must evaluate whether demand can sufficiently meet the increased supply.
@@
 
-To maximize this potential and leverage its prime location, Broadway could adopt targeted strategies to make attending shows more convenient and appealing for holiday visitors.
+To fully utilize its prime location, Broadway could implement targeted strategies to make attending shows more convenient and attractive for holiday visitors.
 For example, collaborating with hotels, travel agencies, and tourism boards to create holiday packages that include show tickets could firmly establish Broadway as an essential part of the holiday itinerary.
@@
 
-## Sustaining Broadway’s Growth in a Rapidly Changing World
+## Sustaining Broadway’s Growth in the Changing World
 
@@
 For instance, the sharp decline in 2016 weekly gross during winter was influenced by a severe snowstorm that forced theaters to close, disrupting public transportation and preventing both audiences and performers from attending.
-Similarly, the slight downturn in 2019 coincided with the onset of the COVID-19 pandemic, which had a profound impact on Broadway operations, highlighting the industry’s vulnerability to external shocks.
+Similarly, the slight downturn in 2019 coincided with the onset of the COVID-19 pandemic, which led to theater closures, halted performances, and a collapse in ticket sales, exposing Broadway’s reliance on in-person attendance and its vulnerability to external disruptions.
 
@@
 
-While the paper provides valuable insights into revenue drivers, it primarily focuses on direct factors such as ticket price, seating capacity, and performance frequency.
-The dataset lacks critical information such as marketing efforts, show popularity, repeat attendance rates, or audience demographics.
-As a result, the analysis misses deeper insights into other potential variables that could offer a more comprehensive understanding of revenue dynamics.
+The paper provides a detailed analysis of revenue drivers but focuses mainly on direct factors such as ticket prices, seating capacity, and performance frequency.
+The dataset does not include information on marketing efforts, show popularity, repeat attendance rates, or audience demographics.
+As a result, the analysis overlooks other potential variables that could provide a fuller understanding of revenue dynamics.
 
@@
 Another weakness of this study is its exclusive focus on analyzing gross revenue without considering the associated costs of producing and running Broadway shows.
-While understanding revenue drivers is crucial, gross revenue alone does not provide a complete picture of financial performance.
+While understanding revenue drivers is important, gross revenue alone does not provide a complete picture of financial performance.
 Factors such as production expenses, marketing costs, theater rental fees, and operational overhead significantly impact profitability but are not accounted for in this analysis.
@@
 
-Future analyses could also employ more advanced models to address the limitations of linear assumptions.
-For example, exploring non-linear relationships and interaction effects between variables, such as the interplay between ticket prices and theater size or the varying impact of holiday weeks on revenue, could reveal important dynamics.
+Future analyses could examine non-linear relationships and interactions between variables, such as the combined influence of ticket prices and theater size on attendance or how holiday weeks impact revenue differently based on theater capacity, providing a deeper understanding of revenue patterns.
 
@@
 This segmentation would enable more precise strategy recommendations tailored to the specific needs and performance characteristics of different types of Broadway shows.
-Also, combining these advanced analyses with cost considerations would offer a holistic approach to optimizing Broadway’s economic sustainability.
-
+Incorporating these analyses with cost considerations could offer a more detailed approach to optimizing Broadway's economic sustainability.
 \newpage
@@
 The purpose of this appendix is to outline an idealized methodology and survey design to supplement the current analysis of Broadway’s weekly gross revenue.
-By incorporating additional survey data and addressing gaps in the existing dataset, this methodology aims to enhance the understanding of revenue drivers, audience behaviors, and market dynamics.
+By incorporating additional survey data, this methodology aims to enhance the understanding of revenue drivers, audience behaviors, and market dynamics.
 The survey is designed to capture demographic, behavioral, and experiential data that complement the operational metrics already analyzed in the study.
@@
 Random sampling provides a robust foundation for generalizable analysis, capturing a wide range of perspectives and behaviors without targeting specific subgroups.
-By employing this method, the study aims to produce reliable and comprehensive insights into the factors influencing Broadway’s attendance and revenue dynamics.
+This method aims to generate accurate and thorough findings on the factors affecting Broadway’s attendance and revenue dynamics.
 
@@
 ## Survey Design Considerations
-The survey is designed to be comprehensive but concise, ensuring high response rates while capturing actionable data. Key design considerations include:
+The survey is designed to balance thoroughness and brevity, aiming to achieve high response rates while collecting useful data. Important design elements include:
 
-- **Question Types**: A mix of multiple-choice, Likert scale, and open-ended questions to balance structured data collection with qualitative insights.
+- **Question Types**: A combination of multiple-choice, Likert scale, and open-ended questions balances structured data collection with qualitative input.
 - **Clarity**: Simple, jargon-free language to ensure accessibility for diverse audiences.
@@
 
-Besides the dataset used for this study, Broadway also conducts several key surveys to gather comprehensive data on various aspects of Broadway theatre.
+In addition to the dataset used for this study, Broadway conducts several key surveys to collect detailed information on various aspects of Broadway theater.
 However, the information and datasets collected through these surveys are not publicly accessible for analysis.
 If this data were made available, merging it with the current dataset could provide a more robust model for gross analysis.
-These surveys include **The Demographics of the Broadway Audience**, which is designed to provide insights into the composition and behavior of Broadway theatregoers.
+These surveys include **The Demographics of the Broadway Audience**, designed to analyze the composition and behavior of Broadway theatergoers.
 
@@
 Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway.
-These surveys and studies help capture broader insights into Broadway's influence and reach, contributing to a more comprehensive understanding of its role in the cultural and economic landscape.
+These surveys and studies provide a broader understanding of Broadway's influence and reach, offering a more complete view of its cultural and economic significance.
 
@@
 Additionally, the trend observed in the Scale-Location plot suggests heteroscedasticity.
-Furthermore, the Residuals vs Leverage plot reveals points with high leverage and large residuals, indicating potential outliers that may disproportionately influence the model.
+Furthermore, the Residuals vs Leverage plot shows points with high leverage and large residuals, indicating potential outliers that may disproportionately influence the model.
 

### 2024-12-02 paper/paper.qmd
Refine the paper, adding references and relevant literature
Revise the paper by adding a more detailed caption, refining the estimand, and improving the discussion section. Enhance the abstract and findings by incorporating specific numbers and results from the study.

@@
 title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
-subtitle: "Positive Effects of Pricing, Seats, Performances, and Holidays, with Limited Impact During Tony Award Months"
+subtitle: "Optimizing Revenue Per Seat While Addressing Modest Holiday Gains and Revenue Declines in Tony Award Months"
 author: "Xuanel Zhou"
-thanks: "Code and data are available at:https://github.com/Isazhou13/Broadway_Gross"
+thanks: "Code and data are available at: [Broadway_Gross](https://github.com/Isazhou13/Broadway_Gross)."
 date: today
@@
 toc: true
-abstract: "This study examines the key factors influencing Broadway’s weekly gross revenue using datasets from Playbill and The Broadway League.
-The result shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact gross, while Tony Award months show limited effects.
-Despite steady long-term growth, disruptions such as the 2016 snowstorm and COVID-19 highlight the industry’s vulnerability to external shocks.
-These findings provide actionable strategies, including holiday-focused marketing, and enhanced engagement during award seasons, to sustain growth and optimize Broadway’s financial performance."
+abstract: "This study employs multiple linear regression to examine factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months.
+A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity.
+Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge reveals untapped potential for Broadway to enhance its appeal as a premier holiday destination.
+Conversely, Tony Award months are linked to a $7,140 decline in weekly revenue, highlighting the need to reposition the awards season as an industry-wide promotional opportunity to benefit all productions."
 format: pdf
@@
 
-Broadway is a cultural and economic landmark in New York City, contributing significantly to the city's global reputation and economy.
+Broadway, located in the heart of New York City's Theater District, comprises 41 theaters in Midtown Manhattan, extending from 42nd to 53rd Streets and between 6th and 8th Avenues [@broadway2021].
+Renowned as a cultural and economic landmark, Broadway plays a pivotal role in shaping the city's global reputation and driving its economy.
 For stakeholders, understanding the drivers of Broadway revenue is essential, as it directly informs strategic decisions on pricing, scheduling, and resource allocation to maximize profitability and sustain operations.
-This study aims to identify and quantify the key factors influencing Broadway’s weekly gross revenue, using datasets provided by Playbill and The Broadway League.
+This study seeks to identify and quantify the key factors influencing Broadway’s weekly gross revenue, utilizing datasets created by Alex Cookson [@cookson_broadway_grosses], which are derived from data originally provided by Playbill [@playbill_grosses].
 
-The estimand in this paper represents the weekly gross revenue of Broadway shows.
-Specifically, it examines how variables such as ticket price, theater seating capacity, number of performances, whether it is a holiday week, whether it falls in a Tony Award month, and the year influence weekly gross revenue.
-While the true estimand is unknown, it is approximated using the available data and model assumptions.
-Defining the estimand ensures the model and methodology align with the research objective and facilitates addressing potential biases from data limitations or methodological choices.
+The estimand of interests in this study is the average change in weekly gross revenue for Broadway productions associated with specific predictors, including ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months, while holding other factors constant.
+This measure captures the independent impact of each variable on revenue.
+While the true estimand is inherently unknown due to potential unobserved confounders, it is approximated using multiple linear regression, relying on the available data and model assumptions.
+Clearly defining the estimand ensures the analysis aligns with the research objectives, facilitates interpretation of the relationships between predictors and revenue, and addresses potential biases from factors such as omitted variables or measurement errors, ensuring the findings remain meaningful and relevant for revenue optimization.
 
-The analysis, conducted using a multiple linear regression model, shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway’s weekly gross revenue.
-Conversely, the limited impact of Tony Award months highlights opportunities for growth.
-While steady long-term growth is observed, disruptions such as the 2016 snowstorm and COVID-19 emphasize Broadway’s vulnerability to external shocks.
+The analysis reveals that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway's weekly gross revenue.
+Specifically, each additional performance generates $70,688, while holiday weeks add $16,684 to weekly revenue.
+Conversely, Tony Award months are associated with a $7,240 decline in weekly gross revenue, underscoring the need to adjust strategies to better capitalize on this period.
 
-These findings emphasize both the opportunities and challenges Broadway faces in maximizing its revenue.
-Identifying the factors that drive revenue and highlighting periods of underperformance provide a foundation for adapting to evolving market conditions.
-For instance, additional potential can be realized through strategies such as holiday packages, collaborations with tourism boards, and enhanced on-site experiences.
-To address the low impact of Tony Award months, strategies could include offering exclusive ticket packages and enhancing media engagement to capitalize on the event's visibility.
-In an era of rapid digitalization and shifting consumer preferences, Broadway must innovate and adopt targeted strategies to sustain growth and maintain its position as a global cultural icon.
+These findings highlight both the opportunities and challenges Broadway faces in maximizing its revenue.
+Prioritizing revenue per seat over simply increasing seating capacity offers a more effective approach to boosting Broadway's financial performance.
+Additionally, significant potential can be unlocked through strategies such as holiday packages, partnerships with tourism boards, and enhancing the on-site experience with festive offerings and merchandise.
+To address the negative impact of Tony Award months, initiatives exclusive ticket bundles, targeted promotions, and expanded media engagement can help capitalize on the event’s visibility.
 
@@
 Finally, @sec-discussion explores the key findings, highlights the main takeaways, addresses the study's weaknesses, and outlines potential next steps.
+@sec-Appendix1 contains the idealized survey designed to gather more detailed information, while @sec-Appendix2 provides supplementary information about the current dataset.
+Lastly, @sec-model includes diagnostic analyses of the model.
 
@@
 
-The dataset, sourced from **Playbill**, reflects Broadway weekly grosses as reported by theatres affiliated with The Broadway League.
+The dataset, compiled by Alex Cookson [@cookson_broadway_grosses] and derived from data originally provided by Playbill [@playbill_grosses], represents Broadway's weekly grosses.
 The data cleaning process involved grouping observations and removing missing values.
-The final dataset consists of 14,519 observations across 10 variables: `week_ending`, `week_number`, `weekly_gross`, `avg_ticket_price`, `seats_in_threatre`, `performances`, `year`, `month`, `holiday_week` and `Tony_Award`.
+The final dataset consists of 14,519 observations across 9 variables: `week_number`, `weekly_gross`, `avg_ticket_price`, `seats_in_threatre`, `performances`, `year`, `month`, `holiday_week` and `Tony_Award`.
+The dataset used for this analysis spans from the beginning of 2010 to the end of 2019.
 
@@
 
-The dataset for this study originates from Playbill, which collects information about Broadway shows through direct reporting and partnerships with industry organizations.
-A significant portion of the data, particularly box office grosses and performance metrics, is provided by The Broadway League, a national trade association for the Broadway industry.
+The dataset for this study originates from Playbill [@playbill_grosses], which collects information about Broadway shows through direct reporting and partnerships with industry organizations.
+A significant portion of the data, particularly box office grosses and performance metrics, is provided by The Broadway League [@broadway_statistics], a national trade association for the Broadway industry.
 
 The transformation of real-world phenomena into the dataset begins with data collection.
-The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information.
+The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information [@ibdb_about].
 Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records.
@@
 #| fig-cap: Distribution of Broadway weekly gross.
+Weekly gross revenues predominantly fall between $500,000 and $2,000,000, with the largest concentration near $700,000 and few instances surpassing $3,000,000.
 #| echo: false
@@
 The distribution, shown in @fig-weekly_gross, exhibits a right-skewed pattern.
-Most weeks have revenues ranging between $500,000 and $2,000,000, with a declining frequency as revenue increases.
-The mode of the distribution appears around $2,000,000.
+Most weeks have gross revenue ranging between $500,000 and $2,000,000, with a declining frequency as revenue increases.
+with the highest frequency observed around $700,000.
 A small number of weeks report revenues exceeding $3,000,000, which may represent potential outliers or rare events that warrant further investigation.
@@
 
+@fig-yearly captures the Broadway industry's growth over the decade.
+The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year.
+The chart shows a steady increase in average yearly gross revenue, reflecting overall industry growth.
+From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2019.
+A slight dip in 2020 likely reflects the impact of the COVID-19 pandemic on Broadway operations.
+
 ```{r}
@@
 #| fig-cap: Yearly Gross Revenue Trends for Broadway Productions, spanning from 2010 to 2019.
+Average yearly gross revenue remained relatively stable between 2013 and 2015.
+Outside of this period, the industry experienced growth.
 #| echo: false
@@
     breaks = seq(min(data_yearly$year), max(data_yearly$year), by = 1),  # One tick per year
-    labels = scales::label_number(accuracy = 1)  # Show integer year labels
   ) +
@@
 
-@fig-yearly captures the Broadway industry's growth over the decade.
-The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year.
-The chart shows a steady increase in average yearly gross revenue, reflecting overall industry growth.
-From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2019.
-A slight dip in 2020 likely reflects the impact of the COVID-19 pandemic on Broadway operations.
-
 ```{r}
 #| label: fig-week_ending
-#| fig-cap: Weekly grossfor each Broadway show over time, spanning from 2010 to 2019. Each point represents the gross for a particular week for a specific show.
+#| fig-cap: Weekly gross for each Broadway show over time, spanning from 2010 to 2019.
+Each point represents the gross for a particular week for a specific show.
+Most productions have weekly gross revenues ranging from $300,000 to $2,000,000, though the data becomes more scattered in later years.
 #| echo: false
@@
 ```
-@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $500,000 to $2,000,000, which aligns with the histogram results shown in @fig-weekly_gross.
+@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with the results shown in @fig-weekly_gross.
 However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.
@@
 #| label: fig-avg_ticket_price
-#| fig-cap: Distribution of Average Broadway Ticket Prices
+#| fig-cap: The distribution of average Broadway ticket prices shows that most prices cluster around $100, with a few shows exceeding $500.
 #| echo: false
@@
 #| label: fig-seats_in_theatre
-#| fig-cap: Distribution of Theatre Sizes Based on Number of Seats
+#| fig-cap: Distribution of Theatre Sizes Based on Number of Seats.
+Most productions are held in theaters with seating capacities around 1,200.
+However, there is considerable variation in theater size choices across different productions.
 #| echo: false
@@
 #| label: fig-performances
-#| fig-cap: Distribution of Performances
+#| fig-cap: Distribution of Performances.
+Over 10,000 weeks of shows, most productions adhere to the standard schedule of 8 performances per week.
+Only a small portion of productions deviate from this, with either more or fewer performances in a given week.
 #| echo: false
@@
 #| label: fig-holiday_week
-#| fig-cap: Comparison of Average Weekly Gross Between Holiday and Non-Holiday Weeks
+#| fig-cap: Comparison of Average Weekly Gross Between Holiday and Non-Holiday Weeks.
+This indicates that holiday weeks tend to result in higher weekly gross revenues for Broadway compared to non-holiday weeks.
 #| echo: false
@@
 ```
-Holiday weeks were identified based on the major holidays of the year and include the following:
-New Year’s Week: The week containing January 1st.
+The Holiday Weeks was identified based on the major holidays of the year, as referenced in @stanley2013america, and includes the following:
 
+- New Year’s Week: The week containing January 1st.
 - Independence Day Week: The week of July 4th.
@@
 Non-holiday weeks are defined as all other weeks that do not overlap with these predefined holiday periods.
-
-The weekly gross revenue was aggregated by grouping the data into holiday and non-holiday weeks.
-The average weekly gross revenue for each category was then calculated by summing all weekly gross revenues within the category and dividing by the total number of weeks in that category.
+In addition, the average weekly gross revenue for each category was was calculated by summing all weekly gross revenues within the category and dividing by the total number of weeks in that category.
 
@@
 #| label: fig-Tony_Award
-#| fig-cap: Comparison of Weekly Gross Revenue During Tony Award and Non-Award Months
+#| fig-cap: Comparison of Weekly Gross Revenue During Tony Award and Non-Award Months.
+This indicates that the occurrence of the Tony Awards in a given month does not significantly impact Broadway gross revenues.
 #| echo: false
@@
 ```
-The Tony Awards, formally the Antoinette Perry Award for Excellence in Broadway Theatre, are the highest honors in Broadway, typically held in June to mark the end of the Broadway season.
-Due to COVID-19, the 2020 awards were postponed to September.
+
+According to @hodge202021st, the Tony Awards, established in 1947 by the American Theatre Wing, are Broadway’s highest honors, held annually in June.
+The "Best Musical" award is the most prestigious, significantly enhancing a production's success, with nominees 60% less likely to close and winners three times more likely to remain open, solidifying its status as the pinnacle of Broadway achievement.
 
@@
 
-The objective of this study is to assist Broadway in strategically managing and making decisions to increase gross revenue, making it essential to choose a model that accurately explains the factors influencing revenue.To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.
+The objective of this study is to assist Broadway in strategically managing and making decisions to increase gross revenue, making it essential to choose a model that accurately explains the factors influencing revenue.
+To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.
 
@@
 
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in [Appendix -@sec-model].
 
@@
 Since it is unrealistic for all predictors the intercept serves as a theoretical starting point for the model.
-- Average Ticket Price ($\beta_1$): Measures the change in weekly gross revenue for each one-unit increase in average ticket price, assuming other predictors remain constant.
-- Seats in the Theater ($\beta_2$):Represents the additional revenue associated with a one-unit increase in the seating capacity of the theater, holding other factors constant.
-- Number of Performances ($\beta_3$): Indicates the increase in weekly gross revenue for each additional performance in the week, controlling for other variables.
+- Average Ticket Price ($\beta_1$): Measures the change in weekly gross revenue for each one-dollar increase in average ticket price, assuming all other predictors remain constant.
+- Seats in the Theater ($\beta_2$): Represents the additional revenue generated by each additional seat available in the theater, assuming all other factors remain constant.
+- Number of Performances ($\beta_3$): Indicates the increase in weekly gross revenue for each additional performance in the week for the show, controlling for other variables.
 - Holiday Week ($\beta_4$): Quantifies the difference in weekly gross revenue between holiday weeks and non-holiday weeks, all else being equal.
@@
 
-As anticipated, average ticket price, seating in yheater, and number of performances exhibit significant positive relationships with weekly gross revenue.
+As anticipated, average ticket price, seating in theater, and number of performances exhibit significant positive relationships with weekly gross revenue.
 Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth.
@@
 
-## Balancing Pricing, Seating Capacity, and Performance Frequency
+## Prioritizing Per-Seat Value Over Expanding Seating Capacity
 
-Operational strategies such as ticket pricing, seating capacity, and performance frequency emerged as key drivers of weekly gross revenue, offering actionable opportunities for Broadway to increase earnings.
-The strong impact of average ticket price underscores the importance of implementing demand-based pricing strategies, particularly for popular or limited-run productions, where higher ticket prices can significantly boost revenue with minimal impact on attendance.
-For less popular shows, optimizing affordability could help maintain audience retention while still contributing to overall revenue.
+While increasing seating capacity and performance frequency predictably boosts revenue, the marginal gains from these factors differ significantly depending on audience demand and pricing strategy.
+The revenue per additional seat, estimated at $699.82, is substantially lower than the per-show contribution of $70,688.48 or the impact of a $1 increase in ticket price, which generates $9,168.
+This result reflects that simply increasing seating capacity, without addressing demand or ticket pricing, offers limited revenue gains.
+The impact of additional seats becomes most meaningful only when shows consistently sell out, underscoring the importance of strategies that drive full occupancy.
 
-Maximizing theater utilization through strategic scheduling and venue allocation is key to increasing revenue.
-Larger venues and additional performances can expand audience capacity, but Broadway managers must evaluate whether demand can sufficiently meet the increased supply.
-Additionally, managers must balance these strategies with logistical considerations such as performer availability, production costs, and preserving the quality of the audience experience.
-By carefully aligning pricing strategies with capacity optimization, Broadway can enhance revenue while ensuring sustainable long-term growth.
+The balance between ticket price and capacity is particularly significant, as a smaller venue with higher ticket prices can outperform a larger theater with lower-priced tickets.
+For instance, @leslie2004price demonstrates that optimizing ticket prices across seating sections can generate substantial revenue, often surpassing strategies focused solely on increasing seating capacity.
+Initiatives such as offering premium seating with added amenities, backstage tours, or bundled packages that include dining and entertainment can further enhance revenue while improving the audience experience.
+As emphasized by @ozhegova2018heterogeneity, understanding demand elasticity is essential, as premium seating typically exhibits lower price sensitivity, making it a key factor in strategic pricing decisions.
 
-## Opportunities in Holiday Weeks and Tony Award Months
+## Maximizing Holiday Demand
 
-The model results indicate that while holiday weeks align with the expectation of increased revenue due to higher audience availability, the effects of Tony Award months challenge the assumption that they inherently boost revenue through increased media attention.
+The model results show that holiday weeks increase weekly gross revenue by an average of $16,684, reflecting a notable seasonal boost and aligning with expectations of higher audience availability during festive periods.
+Holiday weeks are a time when families often travel or plan special outings, and New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, bustling holiday markets, and the New Year’s Eve Ball Drop in Times Square.
+This festive atmosphere draws millions of tourists.
+However, the relatively modest increase of $16,684 per week suggests that Broadway may not be fully capitalizing on its unique position as a holiday destination.
+Studies on tourist behavior during holidays indicate that travelers are more inclined to seek unique and memorable experiences during festive periods [@pearce2013minds], creating a prime opportunity for Broadway to enhance its gross revenue and establish itself as a must-visit holiday experience.
 
-During holiday weeks, families often travel or engage in special outings.
-New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, holiday markets, and the New Year’s Eve Ball Drop in Times Square.
-This festive atmosphere draws millions of tourists, creating a significant opportunity for Broadway to boost gross revenue and position itself as a must-visit holiday experience.
+To better take advantage of its location and the influx of holiday visitors, Broadway could implement targeted strategies to make attending shows more convenient and appealing.
+Collaborating with hotels, travel agencies, and tourism boards to offer bundled holiday packages that include show tickets could position Broadway as an essential part of visitors’ holiday itineraries.
+Moreover, enhancing the on-site experience with seasonal concessions, festive decor, and exclusive holiday merchandise could create a more engaging and memorable experience, attracting more visitors and driving additional revenue during this lucrative season.
 
-To fully utilize its prime location, Broadway could implement targeted strategies to make attending shows more convenient and attractive for holiday visitors.
-For example, collaborating with hotels, travel agencies, and tourism boards to create holiday packages that include show tickets could firmly establish Broadway as an essential part of the holiday itinerary.
-Additionally, enhancing the on-site experience with seasonal concessions and festive elements could further help Broadway attract more visitors during this lucrative season.
+## Transforming the Tony Awards as an Industry-Wide Opportunity
 
-For Tony Award months, the data indicates that Broadway gross remains unaffected, challenging the belief that the awards inherently drive revenue through increased media attention.
-While the Tony Awards generate significant publicity, the focus tends to be on a limited number of nominated or winning shows, leaving many other shows relatively unnoticed.
-This concentrated attention may not translate into broader attendance increases across the industry.
-To address this, Broadway could collaborate with media outlets to feature live broadcasts, behind-the-scenes content, and interviews with nominees to create excitement around both the awards and the shows themselves.
-Offering exclusive ticket packages for Tony-nominated shows during the awards season could further incentivize attendance and increase revenue.
+Tony Award months show a negligible or slightly negative impact on overall revenue, with an estimated effect of $-7,140, challenging the assumption that the awards season boosts Broadway’s financial performance.
+However, @boyle2009broadway finds that Tony Awards increase a production’s revenue by 12% in the week immediately following the event.
+This discrepancy likely stems from media attention and ticket sales being concentrated on a few nominated or winning shows, while most productions see little benefit.
+Additionally, @reddy1998exploring highlights the significant role of critics’ reviews in driving Broadway success, further emphasizing the missed opportunity to leverage the publicity generated by the Tony Awards to benefit all productions more broadly.
 
-## Sustaining Broadway’s Growth in the Changing World
-
-The significant positive relationship between year and weekly gross revenue reflects the steady growth of Broadway over the past decade, driven by factors such as rising ticket prices, increased tourism, and the industry’s ability to attract global audiences.
-However, this growth trajectory also have some exceptional cases, and not valid for all time period.
-For instance, the sharp decline in 2016 weekly gross during winter was influenced by a severe snowstorm that forced theaters to close, disrupting public transportation and preventing both audiences and performers from attending.
-Similarly, the slight downturn in 2019 coincided with the onset of the COVID-19 pandemic, which led to theater closures, halted performances, and a collapse in ticket sales, exposing Broadway’s reliance on in-person attendance and its vulnerability to external disruptions.
-
-Even with a generally positive and sustainable long-term growth trend, Broadway must adapt and innovate to keep pace with the rapid changes in today’s society.
-The rise of streaming platforms and the growing popularity of short-form video content present new challenges to live theater, demanding fresh approaches to attract and engage modern audiences.
-By embracing digital innovations while emphasizing the unique, immersive experience of live performances, Broadway can maintain its growth and continue thriving as a global cultural hub.
+Thus, Broadway could transform the Tony Awards into an industry-wide promotional platform by adopting strategies that engage a broader audience and distribute the benefits more equitably, extending beyond just the nominated and award-winning productions.
+Collaborating with media outlets to produce exclusive behind-the-scenes content, interviews with nominees, and live coverage of performances from non-nominated shows could help expand the appeal of the awards season.
+Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue.
+Centralized marketing campaigns emphasizing the diversity and vibrancy of Broadway’s offerings during this period could further drive engagement and ticket sales across the ecosystem.
+By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.
 
@@
 Different types of productions (e.g., musicals, plays, blockbusters, or niche shows) likely have distinct revenue dynamics that are not adequately addressed by a single model.
-
 Moreover, the model does not account for external factors such as economic conditions, competitor pricing, or shifts in tourism trends, all of which could significantly influence Broadway revenue.
@@
 
-Have you seen this show before?
-
-- Yes
-- No
-
 What motivates you to attend Broadway shows? (Check all that apply)
@@
 
+The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection.
+You can access the survey at the following link: [Google Form Survey](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)
+
 \newpage
@@
 If this data were made available, merging it with the current dataset could provide a more robust model for gross analysis.
-These surveys include **The Demographics of the Broadway Audience**, designed to analyze the composition and behavior of Broadway theatergoers.
+These surveys include **The Demographics of the Broadway Audience** [@broadway_demographics_2022], designed to analyze the composition and behavior of Broadway theatergoers.
 
@@
 
-Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway.
+Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway [@broadway_research_reports].
 These surveys and studies provide a broader understanding of Broadway's influence and reach, offering a more complete view of its cultural and economic significance.

### 2024-12-03 paper/paper.qmd
Revise the Result Section
Using modelsummary and modelplot

@@
 library(scales)
+library(modelsummary)
 
@@
 
-This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here] and scales [@scales].
+This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here], scales [@scales], and modelsummary [@modelsummary].
 The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets.
@@
 # Results {#sec-results}
-
-The results of the multiple linear regression model is summarized in the @tbl-modelresults. The result matches with some of our expectations while deviating in other areas.
+The results of the multiple linear regression model are presented in @fig-model, with more detailed information summarized in @tbl-modelresults in [Appendix -@sec-model].
+While some findings align with our expectations, others reveal notable deviations.
 
@@
 Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences.
+Notably, the confidence intervals for these estimates are relatively narrow, suggesting that the relationships are estimated with high precision and are robust.
 
@@
 
-However, the results for Tony Award months diverge from our initial expectations.
-Contrary to the assumption that Tony Award months would boost revenue due to increased demand or publicity, the coefficients for these variables are negative, indicating a slight decrease in weekly gross revenue during these periods.
+The results for Tony Award months diverge from our initial expectations.
+Contrary to the assumption that Tony Award months would boost revenue due to increased demand or publicity, the coefficients for these variables are negative, suggesting a slight decrease in weekly gross revenue during these periods.
+Additionally, the confidence interval for this variable is wide and crosses zero, indicating uncertainty about the direction and magnitude of the effect.
+This suggests that the observed negative coefficient may not represent a consistent trend and warrants caution when interpreting the impact of Tony Award months on revenue.
 
 Lastly, the year variable exhibits a small but positive effect, consistent with the expectation of a gradual upward trend in Broadway revenue over the years.
-This reflects the broader growth of the industry, potentially due to factors such as inflation.
+The relatively narrow confidence interval for this variable provides strong support for the observed trend, likely reflecting the broader growth of the industry due to factors such as inflation or expanding audience engagement.
 Overall, the model confirms some hypotheses while highlighting discrepancies in the data, prompting further discussion and analysis in the next section.
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: Regression Results for Weekly Gross.
-This table displays the coefficients, standard errors, and t-statistics for the multiple linear regression model used to analyze the factors influencing weekly gross for Broadway.
-#| warning: false
+#| label: fig-model
+#| fig-cap: Coefficient plot illustrating the estimated effects of predictor variables on the response variable.
+Each point represents the estimated coefficient, and the horizontal lines denote the 95% confidence intervals for each coefficient.
+Positive values indicate an increasing effect on the response variable, while negative values indicate a decreasing effect.
+#| echo: false
 
@@
 regression_model <- readRDS(here::here("models/regression_model.rds"))
-summary <- summary(regression_model)
-
-# Extract the coefficients and form a table with estimates, standard errors, and t-values
-coefficients_table <- as.data.frame(summary$coefficients[, 1:3])
-
-# Rename the columns
-colnames(coefficients_table) <- c("Coefficient", "Standard Error", "t-Statistic")
-
-# Display the table
-kable(coefficients_table, digits = 2)
-
-```
-
+
+# Create a custom coefficient name mapping
+custom_coef_names <- c(
+  "avg_ticket_price" = "Average Ticket Price",
+  "seats_in_theatre" = "Seats in Theatre",
+  "performances" = "Number of Performances",
+  "holiday_week" = "Holiday Week Indicator",
+  "Tony_Award" = "Tony Award Winner",
+  "year" = "Year"
+)
+
+# Extract the data from the modelplot object for labeling
+plot_data <- modelplot(
+  list("Model Name" = regression_model),
+  coef_map = custom_coef_names
+)$data
+
+# Ensure the terms are ordered and labeled appropriately
+plot_data$term <- factor(plot_data$term, levels = custom_coef_names)
+
+# Generate the coefficient plot with labeled points
+coef_plot <- ggplot(plot_data, aes(x = term, y = estimate)) +
+  geom_point(size = 2.5) +  # Plot the coefficients as points
+  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +  # Add confidence intervals
+  geom_text(aes(label = round(estimate, 2)), vjust = -1, size = 3) +  # Add coefficient labels
+  coord_flip() +  # Flip the axes for better readability
+  theme_minimal() +  # Use a clean theme
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels if needed
+
+# Display the plot
+print(coef_plot)
+```
 # Discussion {#sec-discussion}
@@
 
+\newpage
+## Model Summary
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: Regression Results for Weekly Gross.
+This table displays the coefficients and their confidence intervalsfor the multiple linear regression model used to analyze the factors influencing weekly gross for Broadway.
+#| warning: false
+
+# Load the regression model
+regression_model <- readRDS(here::here("models/regression_model.rds"))
+
+# Create a mapping of old names to new names
+custom_coef_names <- c(
+  "avg_ticket_price" = "Average Ticket Price",
+  "seats_in_theatre" = "Seats in Theatre",
+  "performances" = "Number of Performances",
+  "holiday_week" = "Holiday Week Indicator",
+  "Tony_Award" = "Tony Award Winner",
+  "year" = "Year"
+)
+
+# Generate the summary table with custom coefficient names
+output_table <- modelsummary(
+  list("Multiple Linear Regression" = regression_model), 
+  statistic = "conf.int",
+  coef_map = custom_coef_names, # Apply custom coefficient names
+  output = "kableExtra"
+)
+
+# Display the table
+output_table
+
+```
+
+\newpage
 # Additional Visulization
+
 ```{r}
@@
 ```
+
 \newpage

### 2024-12-03 other/datasheet/datasheet_Broadway.qmd
Update the  reference and citation for Datasheet

@@
 
-Extract of the questions from @gebru2021datasheets.
+This datasheet is the extract of the questions from @gebru2021datasheets. And it was put together with the help of @citeRohan
 
@@
     - The specific creators of the dataset have not been explicitly identified.
-However, it is likely associated with The Broadway League and their Internet Broadway Database (IBDB), the official archive for Broadway theatre information.
+However, it is likely associated with The Broadway League and their Internet Broadway Database (IBDB) [@ibdb_statistics], the official archive for Broadway theatre information.
 IBDB serves as a comprehensive resource for historical and current Broadway data.
@@
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
+
+The raw data and the accompanying data dictionary are provided by @cookson_broadway.
 
@@
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- I downloaded the data from a publicly available GitHub repository, which sourced the information from the Playbill website.
-The link for the GitHub is: https://github.com/tacookson/data/tree/master/broadway-grosses
+	- I obtained the data via third parties.
+I downloaded the data from a publicly available GitHub repository provided by @cookson_broadway, which sourced the information from the Playbill website [@playbill_grosses].
+The link for the GitHub is [broadway_grosses](https://github.com/tacookson/data/tree/master/broadway-grosses).
+The @citeR package is used for downloading the data.
 8.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- Yes. The raw data is saved. It can be accessed at: https://github.com/tacookson/data/blob/master/broadway-grosses/grosses.csv
+	- Yes, the raw data is saved. It can also be accessed at [this link](https://github.com/tacookson/data/blob/master/broadway-grosses/grosses.csv).
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- The software used is R Programming Language. 
+	- The software used is R Programming Language [@citeR]. 
 4. *Any other comments?*
@@
 If so, please provide a description.*
-	- They can contact the Internet Broadway Database using the form available at https://form.jotform.com/broadwayleague/ibdb-contact-form.
+	- They can contact the Internet Broadway Database using the form available [here](https://form.jotform.com/broadwayleague/ibdb-contact-form).
 This form can be used to contact Broadway with questions or to provide additional information.

### 2024-12-03 paper/paper.qmd
Revise the prose of the paper

@@
 toc: true
-abstract: "This study employs multiple linear regression to examine factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months.
+abstract: "This study examines factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months.
 A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity.
-Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge reveals untapped potential for Broadway to enhance its appeal as a premier holiday destination.
+Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge shows untapped potential for Broadway to enhance its appeal as a premier holiday destination.
 Conversely, Tony Award months are linked to a $7,140 decline in weekly revenue, highlighting the need to reposition the awards season as an industry-wide promotional opportunity to benefit all productions."
@@
 
-The estimand of interests in this study is the average change in weekly gross revenue for Broadway productions associated with specific predictors, including ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months, while holding other factors constant.
+The estimand of interest in this study is the average change in weekly gross revenue for Broadway productions, attributed to specific predictors such as ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months, while holding other factors constant.
 This measure captures the independent impact of each variable on revenue.
@@
 
-The analysis reveals that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway's weekly gross revenue.
+The analysis shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway's weekly gross revenue.
 Specifically, each additional performance generates $70,688, while holiday weeks add $16,684 to weekly revenue.
@@
 These findings highlight both the opportunities and challenges Broadway faces in maximizing its revenue.
-Prioritizing revenue per seat over simply increasing seating capacity offers a more effective approach to boosting Broadway's financial performance.
-Additionally, significant potential can be unlocked through strategies such as holiday packages, partnerships with tourism boards, and enhancing the on-site experience with festive offerings and merchandise.
+Prioritizing revenue per seat over simply increasing seating capacity presents a more effective approach to boosting Broadway's financial performance.
+Additionally, significant potential can be unlocked through strategies such as holiday packages, partnerships with tourism boards, and enhancing the on-site experience with festive activities and merchandise.
 To address the negative impact of Tony Award months, initiatives exclusive ticket bundles, targeted promotions, and expanded media engagement can help capitalize on the event’s visibility.
@@
 @sec-model-set-up details the modeling approach, including predictor selection and the regression model structure.
-@sec-results presents the primary findings and outcomes of the model.
+@sec-results presents the outcomes of the model.
 Finally, @sec-discussion explores the key findings, highlights the main takeaways, addresses the study's weaknesses, and outlines potential next steps.
@@
 
-The dataset, compiled by Alex Cookson [@cookson_broadway_grosses] and derived from data originally provided by Playbill [@playbill_grosses], represents Broadway's weekly grosses.
+The dataset, compiled by Alex Cookson [@cookson_broadway_grosses] and derived from data originally provided by Playbill [@playbill_grosses].
 The data cleaning process involved grouping observations and removing missing values.
@@
 The transformation of real-world phenomena into the dataset begins with data collection.
-The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information [@ibdb_about].
+The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using theater programs to document cast and crew information [@ibdb_about].
 Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records.
@@
 
-However, converting real-world phenomena into dataset entries inevitably results in the loss of important contextual details.
-For example, shows offering premium tickets or standing-room sales may disproportionately inflate weekly grosses compared to productions without these options.
+However, converting real-world phenomena into publicly available dataset entries inevitably leads to the loss of important contextual details in such circumstances.
+For example, productions that include premium tickets or standing-room sales may disproportionately increase weekly grosses compared to those without these options.
 While the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, leaving gaps in understanding revenue dynamics.
@@
 
-Background details and diagnostics are included in [Appendix -@sec-model].
-
 The model in this study is designed to predict weekly gross revenue using the following predictors:
@@
 \end{align}
+
+Background details and diagnostics are included in [Appendix -@sec-model].
 
@@
 # Results {#sec-results}
-The results of the multiple linear regression model are presented in @fig-model, with more detailed information summarized in @tbl-modelresults in [Appendix -@sec-model].
-While some findings align with our expectations, others reveal notable deviations.
+The results of the multiple linear regression model are presented in @fig-model, with more detailed information summarized in [Appendix -@sec-model].
+While some findings align with our expectations, others highlight notable deviations.
 
@@
 The revenue per additional seat, estimated at $699.82, is substantially lower than the per-show contribution of $70,688.48 or the impact of a $1 increase in ticket price, which generates $9,168.
-This result reflects that simply increasing seating capacity, without addressing demand or ticket pricing, offers limited revenue gains.
+This result reflects that simply increasing seating capacity, without addressing demand or ticket pricing, results in limited revenue gains.
 The impact of additional seats becomes most meaningful only when shows consistently sell out, underscoring the importance of strategies that drive full occupancy.
@@
 For instance, @leslie2004price demonstrates that optimizing ticket prices across seating sections can generate substantial revenue, often surpassing strategies focused solely on increasing seating capacity.
-Initiatives such as offering premium seating with added amenities, backstage tours, or bundled packages that include dining and entertainment can further enhance revenue while improving the audience experience.
+Initiatives such as providing premium seating with added amenities, backstage tours, or bundled packages that include dining and entertainment can further enhance revenue while improving the audience experience.
 As emphasized by @ozhegova2018heterogeneity, understanding demand elasticity is essential, as premium seating typically exhibits lower price sensitivity, making it a key factor in strategic pricing decisions.
@@
 To better take advantage of its location and the influx of holiday visitors, Broadway could implement targeted strategies to make attending shows more convenient and appealing.
-Collaborating with hotels, travel agencies, and tourism boards to offer bundled holiday packages that include show tickets could position Broadway as an essential part of visitors’ holiday itineraries.
+Collaborating with hotels, travel agencies, and tourism boards to provide bundled holiday packages that include show tickets could position Broadway as an essential part of visitors’ holiday itineraries.
 Moreover, enhancing the on-site experience with seasonal concessions, festive decor, and exclusive holiday merchandise could create a more engaging and memorable experience, attracting more visitors and driving additional revenue during this lucrative season.
@@
 This discrepancy likely stems from media attention and ticket sales being concentrated on a few nominated or winning shows, while most productions see little benefit.
-Additionally, @reddy1998exploring highlights the significant role of critics’ reviews in driving Broadway success, further emphasizing the missed opportunity to leverage the publicity generated by the Tony Awards to benefit all productions more broadly.
+Additionally, @reddy1998exploring highlights the significant role of critics’ reviews in driving Broadway success, further emphasizing the missed opportunity to use the publicity generated by the Tony Awards to benefit all productions more broadly.
 
@@
 Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue.
-Centralized marketing campaigns emphasizing the diversity and vibrancy of Broadway’s offerings during this period could further drive engagement and ticket sales across the ecosystem.
+Centralized marketing campaigns highlighting the diversity and vibrancy of Broadway’s productions during this period could further enhance engagement and boost ticket sales across the ecosystem.
 By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.
@@
 This segmentation would enable more precise strategy recommendations tailored to the specific needs and performance characteristics of different types of Broadway shows.
-Incorporating these analyses with cost considerations could offer a more detailed approach to optimizing Broadway's economic sustainability.
+Incorporating these analyses with cost considerations could provide a more detailed approach to optimizing Broadway's economic sustainability.
 \newpage
@@
 - To identify purchasing behaviors, such as repeat attendance, pricing sensitivity, and group sales, providing a foundation for refining marketing and pricing strategies.
-- To assess audience motivations and satisfaction, focusing on factors driving show selection and overall theater experience, offering guidance on how to improve Broadway’s organizational and operational strategies.
+- To assess audience motivations and satisfaction, focusing on factors driving show selection and overall theater experience, providing guidance on how to improve Broadway’s organizational and operational strategies.
 
@@
 
-Our sampling strategy utilizes **random sampling** to ensure unbiased representation of Broadway audiences.
+Our sampling strategy utilizes ** simple random sampling** to ensure unbiased representation of Broadway audiences.
 This approach randomly selects participants from the overall population of Broadway ticket buyers and attendees, minimizing potential biases and ensuring the sample reflects the diversity of the audience.
 
-Random sampling provides a robust foundation for generalizable analysis, capturing a wide range of perspectives and behaviors without targeting specific subgroups.
+Random sampling provides a robust foundation for generalizable analysis, capturing a wide range of perspectives and behaviors without targeting specific subgroups [@noor2022simple].
 This method aims to generate accurate and thorough findings on the factors affecting Broadway’s attendance and revenue dynamics.
@@
 - **Tourism Partnerships**: Collaborations with NYC tourism boards, hotels, and travel agencies to engage out-of-town visitors.
-- **Incentives**: Offering discounts on future ticket purchases or exclusive merchandise as incentives for survey participation.
+- **Incentives**: Providing discounts on future ticket purchases or exclusive merchandise as incentives for survey participation.
 
@@
 
-The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection.
+The survey will be implemented via **Google Forms**, which provids a cost-effective platform for data collection.
 You can access the survey at the following link: [Google Form Survey](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)
@@
 
-- **Sampling Method**: The survey is typically conducted annually, with performances selected quarterly to ensure a representative sample of Broadway's diverse offerings.
+- **Sampling Method**: The survey is typically conducted annually, with performances selected quarterly to ensure a representative sample of Broadway's diverse productions.
 This approach captures seasonal variations in the audience and provides a balanced dataset
@@
 Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway [@broadway_research_reports].
-These surveys and studies provide a broader understanding of Broadway's influence and reach, offering a more complete view of its cultural and economic significance.
+These surveys and studies provide a broader understanding of Broadway's influence and reach, presenting a more complete view of its cultural and economic significance.
 
@@
 #| fig-cap: Average Weekly Gross Revenue Trends Across Months, spanning from 2010 to 2019.
+The visualization highlights both year-to-year growth and recurring seasonal patterns in Broadway's revenue performance.
+Notable peaks in revenue are observed around December, coinciding with the holiday season, and slight increases can also be seen during the summer months, potentially due to higher tourist activity.
 #| echo: false

### 2024-12-13 paper/paper.qmd
Update the typos in the paper

@@
 author: "Xuanel Zhou"
-thanks: "Code and data are available at: [Broadway_Gross](https://github.com/Isazhou13/Broadway_Gross)."
+thanks: "Code and data are available at: [Broadway Gross](https://github.com/Isazhou13/Broadway_Gross)."
 date: today
@@
 toc: true
-abstract: "This study examines factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months.
+abstract: "This study examines factors influencing weekly gross revenue on Broadway, focusing on key predictors including average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months.
 A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity.
@@
 This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here], scales [@scales], and modelsummary [@modelsummary].
+
 The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets.
@@
 However, converting real-world phenomena into publicly available dataset entries inevitably leads to the loss of important contextual details in such circumstances.
-For example, productions that include premium tickets or standing-room sales may disproportionately increase weekly grosses compared to those without these options.
-While the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, leaving gaps in understanding revenue dynamics.
+For example, while the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, making it challenging to fully understand revenue dynamics.
 Similarly, discounts and promotions, such as rush tickets or group sales, can lower the average ticket price, potentially underestimating the perceived value of tickets sold.
@@
 The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year.
-The chart shows a steady increase in average yearly gross revenue, reflecting overall industry growth.
-From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2019.
-A slight dip in 2020 likely reflects the impact of the COVID-19 pandemic on Broadway operations.
+It shows a steady increase in average yearly gross revenue, reflecting overall industry growth.
+From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2018.
 
@@
 ```
-@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with the results shown in @fig-weekly_gross.
+@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with @fig-weekly_gross.
 However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.
@@
 ```
-@fig-avg_ticket_price shows the majority of average ticket prices are concentrated around $100, with a peak frequency between $80 and $120.
+@fig-avg_ticket_price shows most average ticket prices are concentrated around $100, with a peak frequency between $80 and $120.
 The right skewed distribution, indicating that while most ticket prices are relatively affordable, there are instances of higher ticket prices extending beyond $300, with a few exceeding $500.
@@
 ```
-@fig-performances highlights the consistency in Broadway’s performance schedules, with the vast majority of shows performing 8 times per week, reaching a frequency of over 10,000 occurrences.
+@fig-performances highlights the consistency in Broadway’s performance schedules, with most shows performing 8 times per week, reaching a frequency of over 10,000 occurrences.
 A small number of shows have fewer or occasionally more than 8 performances per week, likely due to special events, holidays, or production adjustments.
@@
 This festive atmosphere draws millions of tourists.
+
 However, the relatively modest increase of $16,684 per week suggests that Broadway may not be fully capitalizing on its unique position as a holiday destination.
@@
 Collaborating with media outlets to produce exclusive behind-the-scenes content, interviews with nominees, and live coverage of performances from non-nominated shows could help expand the appeal of the awards season.
+
 Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue.
-Centralized marketing campaigns highlighting the diversity and vibrancy of Broadway’s productions during this period could further enhance engagement and boost ticket sales across the ecosystem.
 By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.
@@
 
-Our sampling strategy utilizes ** simple random sampling** to ensure unbiased representation of Broadway audiences.
+Our sampling strategy utilizes **simple random sampling** to ensure unbiased representation of Broadway audiences.
 This approach randomly selects participants from the overall population of Broadway ticket buyers and attendees, minimizing potential biases and ensuring the sample reflects the diversity of the audience.
@@
 The survey will be implemented via **Google Forms**, which provids a cost-effective platform for data collection.
-You can access the survey at the following link: [Google Form Survey](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)
+You can access the survey at the following link: [Google Form - Broadway Audience Survey Form](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)
 
